Paper

### 2020-04-16 Paper.Rmd
Updating Paper with new reference and change in the decay data set
Adding first draft of ATM dataset

@@

>>>>

Risk assessment parameters
@AuYeung2008  -> fractional surface area of finger
@

@@

He et al. analized the patterns of viral sheddin of 94 COVID-19 patients. They also suggested substantial presymptomatic transmission @He2020. "we have estimated that viral shedding of patients
with laboratory-confirmed COVID-19 peaked on or before symptom onset, and a substantial proportion of transmission probably occurred before first symptoms in the index case. More inclusive criteria for contact tracing to capture potential transmission events 2 to 3 days before symptom onset should be urgently considered for effective control of the outbreak"
